---
title: "Case Study 2"
author: "Chad Reo"
date: "8/15/2020"
output: html_document
---



## R Markdown

This Case Study is a deep dive into Talent Management information for DDS Analytics. The objectives of this project are to
1. Identify overall attrition trends
2. Name top three factors that contribute to turnover
3. Create a model to predict Attrition
4. Create a model to predict Income

A video of this presentation can be found here:  https://youtu.be/AbNwj4uWUTY
 

```
# Import necessary libraries

```

## Load Libraries

```{r, echo=FALSE}
library(tidyverse)
library(caret)
library(class)
library(dplyr)
library(ggplot2)
library(grid)
library(gridExtra)
library(Hmisc)
library(jsonlite)
library(kableExtra)
library(knitr)
library(maps)
library(naniar)
library(stringr)
library(tidyr)
library(ISLR)
library(GGally)
library(MASS)
library(car)
library(glmnet)
library(epitools)
library(ROCR)
```
Load files and review formats
```{r, echo=FALSE}
AttritionData <- read.csv('CaseStudy2-data.csv')
head(AttritionData)

# Always important to look at the basic structure first
str(AttritionData) # Attrition and associated Facts/Dimensions: 2 factor columns, 3 num columns, and 4 int columns
AttritionData$ID = as.character(AttritionData$ID) #change ID to Char from Factor
str(AttritionData)

summary(AttritionData) # I see no NAs but some Factors need casting and some number ranges that need normalizing
AttritionData$ID = as.character(AttritionData$ID) #change ID to Char from Factor
AttritionData$LogMonthlyIncome = log10(AttritionData$MonthlyIncome) #Normalize
  
summary(AttritionData)

#on ppt
gg_miss_var(AttritionData)
```

create transformed data for Attrtion analysis
```{r, echo=FALSE}

Attrition_Subset <- sqldf(" Select id, Attrition,
                          
                          case when Attrition = 'No' then 0
                              else 1 end 
                                as 'AttritionCnt', 
                                
                          case when BusinessTravel = 'Travel_Rarely' then 2
                              when BusinessTravel = 'Non-Travel' then 1 
                              else 3 end 
                                as 'BusinessTravelLvl',
                                
                          case when Department = 'Research & Development' then 1
                              when Department = 'Human Resources' then 2 
                              else 3 end 
                                as 'DeptTurnoverLvl',
                                
                          case when DistanceFromHome > 15 then 2
                              else 1 end 
                                as 'DistanceLevel',      
                          
                          case when EducationField in ('Life Sciences','Medical') then 1
                              when EducationField in ('Marketing','Other') then 2 
                              else 3 end 
                                as 'EducAttrLvl',
                          
                          case when JobInvolvement = 4 then 1
                              when JobInvolvement in (2,3) then 2
                              else 3 end 
                                as 'JobInvolvementLvl',      
                          
                          case when JobLevel = 4 then 1
                              when JobLevel in (2,3,5) then 2
                              else 3 end 
                                as 'JobLevelGrp',      
                          
                          case when JobRole like '%Director%' then 1
                              when JobRole in ('Healthcare Representative','Manager') then 2
                              when JobRole = 'Sales Representative' then 4
                              else 3 end 
                                as 'JobRoleLvl',
                          
                           case when JobSatisfaction = 4 then 1
                              when JobSatisfaction = 1 then 3
                              else 2 end 
                                as 'JobSatisfactionLvl',
                          
                          case when MaritalStatus = 'Divorced' then 1
                              when MaritalStatus = 'Married' then 2
                              else 3 end 
                                as 'MaritalStatusLvl',
                                
                          case when MonthlyIncome >10000 then 1
                              else 2 end 
                                as 'IncomeGroup',
                                
                          case when NumCompaniesWorked in (0,2,3,4) then 1
                              when NumCompaniesWorked in (1,8) then 2
                              else 3 end 
                                as 'NumCompaniesWorkedLvl',      
                          
                           case when OverTime = 'No' then 1
                              else 2 end 
                                as 'OverTimeFactor',
                           
                           case when PercentSalaryHike in (21,25) then 1
                              when PercentSalaryHike in (12,14,15,18,19,20) then 2
                              when PercentSalaryHike in (11,13,16,17,22) then 3
                              else 4 end 
                                as 'PercentSalaryHikeLvl', 
                           
                           case when StockOptionLevel in (2,1) then 1
                              else 2 end 
                                as 'StockOptionGrp',
                                
                            case when TotalWorkingYears >25 then 1
                              when TotalWorkingYears in (9,13,10,19,24,12,15,22,21,17,20) then 2
                              when TotalWorkingYears in (11,14,26,16,23,18,8,25,31) then 3
                              when TotalWorkingYears in (6,5,7,4,3) then 4
                              else 5 end 
                                as 'WorkYrsGroupLvl',
                            
                            case when TrainingTimesLastYear in (0,1,2) then 2
                              else 1 end 
                                as 'TrainingTimesGrp',  
                                
                            case when WorkLifeBalance = 1 then 2
                              else 1 end 
                                as 'WorkLifeBalanceGrp',     
                                
                            case when YearsAtCompany <= 5 then 2
                              else 1 end 
                                as YearsAtCompanyLvl,
                            
                            case when YearsSinceLastPromotion between 6 and 10 then 2
                              else 1 end 
                                as YearsSinceLastPromotionLvl,
                                
                                Education,
                                TotalWorkingYears,
                                YearsAtCompany,
                                YearsInCurrentRole,
                                YearsSinceLastPromotion,
                                YearsWithCurrManager,
                                Department,
                                YearsSinceLastPromotion/TotalWorkingYears as CurrPrcntOfOverall,
                                YearsSinceLastPromotion/YearsInCurrentRole as NewRolePrcnt,
                                YearsSinceLastPromotion/TotalWorkingYears as PercntWaiting,
                                LogMonthlyIncome,
                                Gender,
                                Age,
                                DistanceFromHome
                                
                          from AttritionData
                        ")
Attrition_Subset
summary(Attrition_Subset)
```


Data Exploration


```{r, echo=FALSE}

                        
#Overall                     
Attrition_Subset_qry1 <- sqldf("select count(ID) as EmplCnt,
                            Sum(AttritionCnt) as AttritionCnt
                        From Attrition_Subset")
Attrition_Subset_qry1$AttritionPrcnt = as.numeric(Attrition_Subset_qry1$AttritionCnt/Attrition_Subset_qry1$EmplCnt)
Attrition_Subset_qry1 

#graph overall
barplot(Attrition_Subset_qry1$AttritionPrcnt,
        main="Overall Attrition %",
        ylab="Percent",
        border="red",
        col="blue",
        density=10)   




#By Department                                                
Attrition_Subset_qry2 <- sqldf("select Department, 
                            count(ID) as EmplCnt,
                            Sum(AttritionCnt) as AttritionCnt
                        From Attrition_Subset 
                        Group by Department
                        Order by Department")
Attrition_Subset_qry2$AttritionPrcnt = as.numeric(Attrition_Subset_qry2$AttritionCnt/Attrition_Subset_qry2$EmplCnt)
Attrition_Subset_qry2  

barplot(Attrition_Subset_qry2$AttritionPrcnt,
        main="Attrition by Department",
        names.arg=c("Human Resources","Research & Devl","Sales"), 
        ylab="Percent",
        border="red",
        col="blue",
        density=10) 


#By Department by Gender
Attrition_Subset_qry3 <- sqldf("select Department, 
                            count(ID) as EmplCnt,
                            Sum(AttritionCnt) as AttritionCnt,
                            Gender
                        From Attrition_Subset 
                        Group by Department, Gender
                        Order by Gender, Department")
Attrition_Subset_qry3$AttritionPrcnt = as.numeric(Attrition_Subset_qry3$AttritionCnt/Attrition_Subset_qry3$EmplCnt)
Attrition_Subset_qry3 


#Attrition by Department by Gender
barplot(Attrition_Subset_qry3$AttritionPrcnt,
        main="Attrition by Department",
        names.arg=c("HR-F","R&D-F","Sales-F",
                    "HR-M","R&D-M","Sales-M"), 
        las = 1,
        horiz=T,
        beside=TRUE,
        xlab="Percent",
        border="red",
        col="blue",
        density=10) 




Attrition_Subset_qry3 %>% #filter(Attrition_Subset_qry$Gender == "Female") %>%
  ggplot(aes(x = factor(Department), y = AttritionPrcnt, color = Gender)) +
  geom_bar(stat="identity", position="stack") +
  ggtitle("Attrition by Dept by Gender") +
  xlab("Department") + ylab("Attrition %")



Attrition_Subset_qry <- sqldf("select Department, gender,
                            count(ID) as EmplCnt,
                            Sum(AttritionCnt) as AttritionCnt,
                            DistanceLevel,
                            JobInvolvementLvl,
                            WorkLifeBalanceGrp
                        From Attrition_Subset 
                        Group by Department, gender")
Attrition_Subset_qry$AttritionPrcnt = as.numeric(Attrition_Subset_qry$AttritionCnt/Attrition_Subset_qry$EmplCnt)
Attrition_Subset_qry 

install.packages("viridis")
library(viridis)

Attrition_Subset_qry %>% ggplot(aes( x=Department, y=AttritionPrcnt)) + 
  geom_bar(stat="identity", color="white", fill="blue") +
  scale_fill_viridis(discrete = T) +
  ggtitle("Studying 4 species..") +
  #theme_ipsum() +
  xlab("")

```


Look at individual factors  
```{r, echo=FALSE}
                        
                      
Attrition_Subset_qry %>% ggplot(aes(x = Department, 
      y = AttritionPrcnt)) +  #, color = Gender
      geom_point(aes(shape = Gender), size = 3) +
      ggtitle("Attrition by Department by Distance From Home") + 
      xlab("Department") + ylab("Distance From Home")                         
                        

Attrition_Subset %>% ggplot(aes(YearsAtCompany,LogMonthlyIncome))+geom_point(color = )+
  geom_smooth(method='lm',formula=Attrition_Subset$YearsAtCompany~Attrition_Subset$LogMonthlyIncome)                        
                        
                        
                        
#Look at individual factors  
gridExtra::grid.arrange(
Attrition_Subset %>% ggplot(aes(x = factor(Department), 
    y = DistanceFromHome, color = Attrition)) +
   geom_jitter(aes(shape = Gender), size = 3) +
   ggtitle("Attrition by Department by Distance From Home") + 
   xlab("Department") + ylab("Distance From Home") ,
                        
Attrition_Subset %>% ggplot(aes(x = factor(Department), 
                y = BusinessTravelLvl, color = Attrition)) +
    geom_jitter(aes(shape = factor(Gender)), size = 3) +
    ggtitle("Attrition by Department by Travel Level") + 
    xlab("Department") + ylab("Travel Level")  ,
nrow = 1
)

gridExtra::grid.arrange(
Attrition_Subset %>% 
  ggplot(aes(x = factor(Department), 
             y = Education, color = Attrition)) +
  geom_jitter(aes(shape = factor(Gender)), size = 3) +
  ggtitle("Attrition by Department by Education") + 
  xlab("Department") + ylab("Education")  ,

#compare
Attrition_Subset %>% 
  ggplot(aes(x = YearsWithCurrManager, 
             y = Age, color = Attrition)) +
  geom_jitter(aes(shape = Gender), size = 3) +
  ggtitle("Attrition by Job Role and Job Level") + 
  xlab("Job Role Level") + ylab("Job Level Group") ,
nrow  = 1
)



#Look at individual factors                        
Attrition_Subset %>% ggplot(aes(x = factor(Attrition_Subset$BusinessTravelLvl), y = YearsInCurrentRole, color = Attrition)) + geom_jitter()

#Combine factors                           
Attrition_Subset %>% ggplot(aes(x = DeptTurnoverLvl, y = EducAttrLvl, color = Attrition)) + geom_jitter()
                        
Attrition_Subset %>% ggplot(aes(x = OverTimeFactor, y = Department, color = Attrition)) + geom_jitter()
                         
Attrition_Subset %>% ggplot(aes(x = JobLevelGrp, y = MaritalStatusLvl, color = Attrition)) + geom_jitter()

#for SalesReps LogYearsAtCompany * LogMonthlyIncome 
Attrition_Subset %>% ggplot(aes(x = NumCompaniesWorkedLvl, y = WorkLifeBalanceGrp, color = Attrition)) + geom_jitter()

```


```{r, echo=FALSE}
#create data set for knn                       
Attrition_Subset_for_test <- sqldf("select BusinessTravelLvl*
  DeptTurnoverLvl*
  DistanceLevel*
  EducAttrLvl*
  JobInvolvementLvl*
  JobLevelGrp*
  JobRoleLvl*
  JobSatisfactionLvl*
  MaritalStatusLvl*
    IncomeGroup as measure1,
 
  NumCompaniesWorkedLvl*
  OverTimeFactor*
  NumCompaniesWorkedLvl*
  PercentSalaryHikeLvl*
  StockOptionGrp*
  WorkYrsGroupLvl*
  TrainingTimesGrp*
  WorkLifeBalanceGrp*
  YearsAtCompanyLvl*
  YearsSinceLastPromotionLvl as measure2,

  Attrition
  from Attrition_Subset")





##create normalization function
nor <-function(x) { (x -min(x))/(max(x)-min(x))   }

##Run nomalization on first 2 coulumns of dataset because they are the predictors
Attrition_Subset_for_test_norm <- as.data.frame(lapply(Attrition_Subset_for_test[,c(1,2)], nor))

summary(Attrition_Subset_for_test_norm)
str(Attrition_Subset_for_test_norm)

#train and test datasets
trainIndices = sample(1:dim(Attrition_Subset_for_test)[1],round(splitPerc * dim(Attrition_Subset_for_test)[1]))
train = Attrition_Subset_for_test_norm[trainIndices,]
test = Attrition_Subset_for_test_norm[-trainIndices,]

##extract 3th column of train dataset because it will be used as 'cl' argument in knn function.
Attrition_target_category <- Attrition_Subset_for_test[trainIndices,3]
##extract 3th column of test dataset to measure the accuracy
Attrition_test_category <- Attrition_Subset_for_test[-trainIndices,3]

#set table to record measures
accs = data.frame(accuracy = numeric(30),
                  k = numeric(30),
                  sensitivity = numeric(30),
                  specificity = numeric(30))

for(i in 1:30)
{
  classifications = knn(train[,c(1,2)],test[,c(1,2)],Attrition_target_category, prob = TRUE, k = i)
  table(Attrition_test_category,classifications)
  CM = confusionMatrix(table(Attrition_test_category,classifications))
  accs$accuracy[i] = CM$overall[1]
  accs$sensitivity[i] = CM$byClass[1]
  accs$specificity[i] = CM$byClass[2]
  accs$k[i] = i
}

plot(accs$k,accs$accuracy, type = "l", xlab = "k")
plot(accs$k,accs$sensitivity, type = "l", xlab = "k")
plot(accs$k,accs$specificity, type = "l", xlab = "k")



# Loop for many k and the average of many training / test partition
#```{r}
iterations = 500
numks = 30

masterAcc = matrix(nrow = iterations, ncol = numks)
masterSensitivity = matrix(nrow = iterations, ncol = numks)
masterSpecificity = matrix(nrow = iterations, ncol = numks)


for(j in 1:iterations)
{

  trainIndices = sample(1:dim(Attrition_Subset_for_test)[1],round(splitPerc * dim(Attrition_Subset_for_test)[1]))
  train = Attrition_Subset_for_test_norm[trainIndices,]
  test = Attrition_Subset_for_test_norm[-trainIndices,]
  train_var = Attrition_Subset_for_test[trainIndices,3]
  test_var = Attrition_Subset_for_test[-trainIndices,3]
  
  for(i in 1:numks)
  {
    classifications = knn(train[,c(1,2)],test[,c(1,2)],train_var, prob = TRUE, k = i)
    table(test_var,classifications)
    CM = confusionMatrix(table(test_var,classifications))
    #masterAcc[j,i] = CM$byClass[2]
    masterAcc[j,i] = CM$overall[1]
    masterSensitivity[j,i] = CM$byClass[1]
    masterSpecificity[j,i] = CM$byClass[2]
    #accs$k[j,i] = j,i
  }
  
}

MeanAcc = colMeans(masterAcc)
MeanSensitivity= colMeans(masterSensitivity)
MeanSpecificity = colMeans(masterSpecificity)

#Show plots of the Accuracy, Sensitivity, and Specificity

plot(seq(1,numks,1),MeanAcc, col="blue", type = "l", main = "KNN Accuracy")
plot(seq(1,numks,1),MeanSensitivity, col="orange", type = "l", main = "KNN Sensitivity")
plot(seq(1,numks,1),MeanSpecificity, col="green", type = "l",  main = "KNN Specificity")

```


import predict data

```{r, echo=FALSE}



AttritionData_Predict <- read.csv('CaseStudy2CompSet No Attrition.csv')

summary(AttritionData_Predict)
str(AttritionData_Predict)

Attrition_Subset_Predict <- sqldf(" Select id,
                          case when BusinessTravel = 'Travel_Rarely' then 2
                              when BusinessTravel = 'Non-Travel' then 1 
                              else 3 end 
                                as 'BusinessTravelLvl',
                                
                          case when Department = 'Research & Development' then 1
                              when Department = 'Human Resources' then 2 
                              else 3 end 
                                as 'DeptTurnoverLvl',
                                
                          case when DistanceFromHome > 15 then 2
                              else 1 end 
                                as 'DistanceLevel',      
                          
                          case when EducationField in ('Life Sciences','Medical') then 1
                              when EducationField in ('Marketing','Other') then 2 
                              else 3 end 
                                as 'EducAttrLvl',
                          
                          case when JobInvolvement = 4 then 1
                              when JobInvolvement in (2,3) then 2
                              else 3 end 
                                as 'JobInvolvementLvl',      
                          
                          case when JobLevel = 4 then 1
                              when JobLevel in (2,3,5) then 2
                              else 3 end 
                                as 'JobLevelGrp',      
                          
                          case when JobRole like '%Director%' then 1
                              when JobRole in ('Healthcare Representative','Manager') then 2
                              when JobRole = 'Sales Representative' then 4
                              else 3 end 
                                as 'JobRoleLvl',
                          
                           case when JobSatisfaction = 4 then 1
                              when JobSatisfaction = 1 then 3
                              else 2 end 
                                as 'JobSatisfactionLvl',
                          
                          case when MaritalStatus = 'Divorced' then 1
                              when MaritalStatus = 'Married' then 2
                              else 3 end 
                                as 'MaritalStatusLvl',
                                
                          case when MonthlyIncome >10000 then 1
                              else 2 end 
                                as 'IncomeGroup',
                                
                          case when NumCompaniesWorked in (0,2,3,4) then 1
                              when NumCompaniesWorked in (1,8) then 2
                              else 3 end 
                                as 'NumCompaniesWorkedLvl',      
                          
                           case when OverTime = 'No' then 1
                              else 2 end 
                                as 'OverTimeFactor',
                           
                           case when PercentSalaryHike in (21,25) then 1
                              when PercentSalaryHike in (12,14,15,18,19,20) then 2
                              when PercentSalaryHike in (11,13,16,17,22) then 3
                              else 4 end 
                                as 'PercentSalaryHikeLvl', 
                           
                           case when StockOptionLevel in (2,1) then 1
                              else 2 end 
                                as 'StockOptionGrp',
                                
                            case when TotalWorkingYears >25 then 1
                              when TotalWorkingYears in (9,13,10,19,24,12,15,22,21,17,20) then 2
                              when TotalWorkingYears in (11,14,26,16,23,18,8,25,31) then 3
                              when TotalWorkingYears in (6,5,7,4,3) then 4
                              else 5 end 
                                as 'WorkYrsGroupLvl',
                            
                            case when TrainingTimesLastYear in (0,1,2) then 2
                              else 1 end 
                                as 'TrainingTimesGrp',  
                                
                            case when WorkLifeBalance = 1 then 2
                              else 1 end 
                                as 'WorkLifeBalanceGrp',     
                                
                            case when YearsAtCompany <= 5 then 2
                              else 1 end 
                                as YearsAtCompanyLvl,
                            
                            case when YearsSinceLastPromotion between 6 and 10 then 2
                              else 1 end 
                                as YearsSinceLastPromotionLvl     
                                
                          from AttritionData_Predict
                        ")
Attrition_Subset_Predict
str(Attrition_Subset_Predict)


Attrition_Subset_for_Predict <- sqldf("select BusinessTravelLvl,
  DeptTurnoverLvl,
  DistanceLevel,
  EducAttrLvl,
  JobInvolvementLvl,
  JobLevelGrp,
  JobRoleLvl,
  JobSatisfactionLvl,
  MaritalStatusLvl,
   NumCompaniesWorkedLvl,
  OverTimeFactor,
  NumCompaniesWorkedLvl,
  PercentSalaryHikeLvl,
  StockOptionGrp,
  WorkYrsGroupLvl,
  TrainingTimesGrp,
  WorkLifeBalanceGrp,
  YearsAtCompanyLvl,
  YearsSinceLastPromotionLvl
  from Attrition_Subset_Predict")
Attrition_Subset_for_Predict


##Run nomalization on first 2 coulumns of dataset because they are the predictors
Attrition_Subset_for_test_norm <- as.data.frame(lapply(Attrition_Subset_for_Predict[,c(1,2)], nor))

```
Attrition Prediction Results

```{r, echo=FALSE}


# k = 15
classifications = knn(train[,c(1,2)],Attrition_Subset_for_test_norm[,c(1,2)],train_var, k = 15)
results = as.data.frame(cbind(Attrition_Subset_Predict$ID,classifications))

Predict_layout <- sqldf("select V1 as ID, 
  case when classifications = 1 then 'No' else 'Yes' end as Attrition
  
  from results")
Predict_layout
str(results)

######
write.csv(Predict_layout, file = "AttritionPredictions.csv")

```


Model for Salary


```{r, echo=FALSE}


Income_Subset <- sqldf(" Select id, 
                                age,
                                DeptTurnoverLvl,
                                JobLevelGrp,
                                JobRoleLvl,
                                WorkYrsGroupLvl,
                                LogMonthlyIncome,
                                TotalWorkingYears
                      from Attrition_Subset
                      ")
str(Income_Subset)
summary(Income_Subset)



# Weight, Acceleration, and Displacement look promising, let's zoom in
Income_Subset %>% ggplot(aes(x=JobLevelGrp, y=LogMonthlyIncome, color=JobRoleLvl)) + geom_jitter() # Increasing SD?
Income_Subset %>% ggplot(aes(x=JobRoleLvl, y=LogMonthlyIncome, color=DeptTurnoverLvl)) + geom_jitter() # Increasing SD?

AttritionData %>% select(Age,YearsAtCompany,YearsInCurrentRole,YearsSinceLastPromotion,TrainingTimesLastYear,PercentSalaryHike)

ggpairs(Attrition_Subset_for_Predict[,-1])

AttritionData$LogMonthlyIncome = log(AttritionData$MonthlyIncome)
# Let's look at distribution of weight and mpg values
hist(AttritionData$MonthlyIncome, main="Monthly Income Distribution", xlab="Monthly Income")
hist((AttritionData$LogMonthlyIncome), main="Log Monthly Income Distribution", xlab="Log Monthly Income")

hist(Income_Subset$WorkYrsGroupLvl, main="Monthly Income Distribution", xlab="Monthly Income")
# Scatter plot to inspect general trend
AttritionData %>% ggplot(aes(x=AttritionData$LogMonthlyIncome, y=AttritionData$TotalWorkingYears, color = Department)) + 
  geom_point() + geom_smooth(method = "lm")+ggtitle("Working Year vs Income")+ylab("Working Years")+xlab("Log Monthly Income")

AttritionData %>% ggplot(aes(x=AttritionData$LogMonthlyIncome, y=AttritionData$DeptTurnoverLv, color = Department)) + 
  geom_point() + geom_smooth(method = "lm")+ggtitle("Working Year vs Income")+ylab("Working Years")+xlab("Log Monthly Income")

```

Split into Test and Train and check output

```{r, echo=FALSE}

set.seed(101) # Set Seed so that same sample can be reproduced in future
#Select 75% of data as sample from total 'n' rows of the data  
sample <- sample.int(n = nrow(Smote), size = floor(.75*nrow(Smote)), replace = F)
Income_train <- Income_Subset[sample, ]
Income_test  <- Income_Subset[-sample, ]


# Use lm to create a linear regression model
fit2 <- lm(LogMonthlyIncome~
             DeptTurnoverLvl+
           JobLevelGrp+
           JobRoleLvl+
           #WorkYrsGroupLvl+
           TotalWorkingYears,
             data=Income_train)
summary(fit2)




formula(fit2)

Model1_Preds = predict(fit2, newdata = Income_test, interval = "prediction")
output <- as.data.frame(Model1_Preds)
output$fit = 10^output$fit
output$lwr = 10^output$lwr
output$upr = 10^output$upr

summary(output)



#check the fit
Test <- cbind(output,MonthlyIncome = 10^Income_test$LogMonthlyIncome)

```

Output for Income File
```{r, echo=FALSE}


###Import 
IncomeData_Predict <- read.csv('CaseStudy2CompSet No Salary.csv')

Income_Subset_Predict <- sqldf(" Select id,
                                
                          case when Department = 'Research & Development' then 1
                              when Department = 'Human Resources' then 2 
                              else 3 end 
                                as 'DeptTurnoverLvl',
                          
                          case when JobLevel = 4 then 1
                              when JobLevel in (2,3,5) then 2
                              else 3 end 
                                as 'JobLevelGrp',      
                          
                          case when JobRole like '%Director%' then 1
                              when JobRole in ('Healthcare Representative','Manager') then 2
                              when JobRole = 'Sales Representative' then 4
                              else 3 end 
                                as 'JobRoleLvl',
                          
                         TotalWorkingYears    
                                
                          from IncomeData_Predict
                        ")
Income_Subset_Predict
str(Income_Subset_Predict)


Model1_Preds = predict(fit2, newdata = Income_Subset_Predict, interval = "prediction")
output <- as.data.frame(Model1_Preds)
output$fit = 10^output$fit
output$lwr = 10^output$lwr
output$upr = 10^output$upr

export <- cbind(ID = Income_Subset_Predict$ID, Income = output$fit)
summary(export)
write.csv(export, file = "Case2PredictionsReo Salary.csv")



# The easy way to get the p-values and confidence intervals
summary(fit2)
confint(fit2)
formula(fit2)
```
